Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-03-15 reports/manuscript.Rmd
Fix typo in manuscript

Children's engagement is a screen time is a complex issue.
Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
Hampering efforts to make an informed decision is the lack of comprehensive evidence.
As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
In this study, we systematically harmonize data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
We show that some forms of screen time---such as social media---show consistent evidence of harm for children, with no clear evidence of a benefit.
Other relationships are more complex.
Video games, for example, are associated with poorer body composition and learning outcomes.
However, video games for a specific educational purpose (such as numeracy) are associated with improvements in that subject area.
Caregivers must therefore weigh the health risk against the educational benefit.
The findings of this study provide parents and other caregivers with the information to make these informed decisions.

@@

While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].
With concerns over the impact of screen use including education, health, social development, and psychological well-being, a broad overview that identifies potential benefits and risks is needed.

>>>>

Children's engagement in screen time is a complex issue.
Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
Hampering efforts to make an informed decision is the lack of comprehensive evidence.
As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
In this study, we systematically harmonize data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
We show that some forms of screen time---such as social media---show consistent evidence of harm for children, with no clear evidence of a benefit.
Other relationships are more complex.
Video games, for example, are associated with poorer body composition and learning outcomes.
However, video games for a specific educational purpose (such as numeracy) are associated with improvements in that subject area.
Caregivers must therefore weigh the health risk against the educational benefit.
The findings of this study provide parents and other caregivers with the information to make these informed decisions.

@@

While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
With concerns over the impact of screen use including education, health, social development, and psychological well-being, a broad overview that identifies potential benefits and risks is needed.
